Stock enhancement undermines community stability

### 2022-02-08 rmd/supporting_info.Rmd
edit: support info

**Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan. The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterresearchinstitutehokkaidoresearchorganizationAnnualReportMonitoring2021]. The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net). Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^). We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period. As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019. Summed abundance of first and second passes was used in the following analysis. **Table S5** summarizes observed species in these watersheds.

**Fish stocking.** The stocking of masu salmon began in the 1950s. Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage). Although the fish release occurs at multiple locations within a watershed, the stocking information is available only at the watershed level. For each release stage, we assembled annual records of stock enhancement (the number of fish released; 1999-2019) from annual investigations by Hokkaido National Research Institute and Salmon and Freshwater Fisheries Research Institute. During the study period, the majority of stocking took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)

>>>>

**Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan. The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterfisheriesresearchinstitutehokkaidoresearchorganizationAnnualReportMonitoring2021]. The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net). Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^). We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period. As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019. Summed abundance of first and second passes was used in the following analysis. **Table S5** summarizes observed species in these watersheds.

**Fish stocking.** The stocking of masu salmon began in the 1950s. Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage). Although the fish release occurs at multiple locations within a watershed, the stocking information is available only at the watershed level. For each release stage, we assembled annual records of stock enhancement (the number of fish released; 1999-2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute. During the study period, the majority of stocking took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)
